Uniformly Ergodic Data-Augmented MCMC for Fitting the General Stochastic Epidemic Model to Incidence Data

### 2021-12-14 Manuscripts/Article/Article.tex

	\begin{figure}
		\centering
		\includegraphics[scale = 0.5]{infection_rate_SIR_PDSIR.jpg}
		\caption{Infection dynamics of the SIR (dashed line) and PD-SIR (solid line) processes in a small population ($(S(0), I(0)) = (10,2)$) with $\beta=1$. The schedule of the PD-SIR is $t_{0:3}=(0, 0.2, 0.4, 0.6)$.
		The vertical dotted lines indicate the infection (red) and removal (blue) times.}
		\label{fig:mu}
	\end{figure}

@@

	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E2_K5}
			\caption{$K = 5$}
			\label{fig:comparison_RD_SIR_K5}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E2_K10}
			\caption{$K = 10$}
			\label{fig:comparison_RD_SIR_K10}
		\end{subfigure}
		\\
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E2_K50}
			\caption{$K = 50$}
			\label{fig:comparison_RD_SIR_K50}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E2_K1000}
			\caption{$K = 1000$}
			\label{fig:comparison_RD_SIR_K1000}
		\end{subfigure}
		\caption{Trajectories of the compartments $S$, $I$ and $R$ in a SIR (in colors) and PD-SIR processes (in grey) with the same infection incidence data $T_{1:K}$.}
		\label{fig:comparison}
	\end{figure}
	\smallskip

@@

	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_trajectories}
			\caption{Compartment trajectories}
			\label{fig:E1_trajectories}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_short_no_burn_gamma_tp}
			\caption{Transient phase}
			\label{fig:E1_short_no_burn_gamma_tp}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_burn_gamma_tp}
			\caption{Recurrent phase}
			\label{fig:E1_burn_gamma_tp}
		\end{subfigure}
		%\hfill
		%\begin{subfigure}[b]{0.24\textwidth}
		%	\centering
		%	\includegraphics[width=\textwidth]{E1_burn_gamma_acf}
		%	\caption{Auto-correlation function for $\gamma$}
		%	\label{fig:E1_burn_gamma_acf}
		%\end{subfigure}
		\caption{Performance of the DA-MCMC in a medium-sized population for the parameter $\gamma$.}
		\label{fig:E1}
	\end{figure}

>>>>

	\begin{figure}
		\centering
		\includegraphics[scale = 0.4]{infection_rate_SIR_PDSIR.jpg}
		\caption{Infection dynamics of the SIR (dashed line) and PD-SIR (solid line) processes in a small population ($(S(0), I(0)) = (10,2)$) with $\beta=1$. The schedule of the PD-SIR is $t_{0:3}=(0, 0.2, 0.4, 0.6)$.
		The vertical dotted lines indicate the infection (red) and removal (blue) times.}
		\label{fig:mu}
	\end{figure}

@@

	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E2_K5}
			\caption{$K = 5$}
			\label{fig:comparison_RD_SIR_K5}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E2_K10}
			\caption{$K = 10$}
			\label{fig:comparison_RD_SIR_K10}
		\end{subfigure}
		\\
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E2_K50}
			\caption{$K = 50$}
			\label{fig:comparison_RD_SIR_K50}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E2_K1000}
			\caption{$K = 1000$}
			\label{fig:comparison_RD_SIR_K1000}
		\end{subfigure}
		\caption{Trajectories of the compartments $S$, $I$ and $R$ in a SIR (in colors, with $S$ in red, $I$ in green and $R$ in blue) and PD-SIR processes (in grey) with the same infection incidence data $I_{1:K}$.}
		\label{fig:comparison}
	\end{figure}
	\smallskip

@@

	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_trajectories}
			\caption{Compartment trajectories ($S$ in red, $I$ in green and $R$ in blue)}
			\label{fig:E1_trajectories}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_short_no_burn_gamma_tp}
			\caption{Transient phase}
			\label{fig:E1_short_no_burn_gamma_tp}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_burn_gamma_tp}
			\caption{Recurrent phase}
			\label{fig:E1_burn_gamma_tp}
		\end{subfigure}
		%\hfill
		%\begin{subfigure}[b]{0.24\textwidth}
		%	\centering
		%	\includegraphics[width=\textwidth]{E1_burn_gamma_acf}
		%	\caption{Auto-correlation function for $\gamma$}
		%	\label{fig:E1_burn_gamma_acf}
		%\end{subfigure}
		\caption{Performance of the DA-MCMC in a medium-sized population for the parameter $\gamma$.}
		\label{fig:E1}
	\end{figure}
